---
title: "linreg"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{linreg}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(linreg)
```

# Introduction

The package `linreg` can be used to estimate linear regression models. It also contains different methods that can be used on a fitted model.

# The linreg function

The `linreg()` function takes two arguments, `formula` and `data`.

In this example we use the built-in `iris` dataset.

```{r}
model <- linreg(Petal.Length ~ Species, data = iris)
```

The model is now saved in the object `model`.

```{r}
class(model)
```

# Methods

The following methods can be used on an object of class `linreg`.

## Print

The `print()` method prints the estimated coefficients.

```{r}
print(model)
```

## Coef

The `coef()` method returns the estimated coefficients.

```{r}
coef(model)
```

## Residuals

The `resid()` method returns the residuals from the model.

```{r}
resid(model)
```

## Predictions

The `pred()` method returns the predicted values from the model.

```{r}
pred(model)
```

## Summary

The `summary()` method gives a summary of the fitted model.

```{r}
summary(model)
```

## Plot

The `plot()` method creates plots for the fitted model.

```{r}
plot(model)
```

# Conclusion

The `linreg()` function can be used to estimate a linear regression model. The different methods can then be used to examine the fitted model and its results.
